---
title: "Statistical report for TEENS feasibility trial"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
subtitle: Using simulated data
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(huxtable)
library(flextable)
source("functions.R")
screened <- 100
n <- 30
source("sim_data.R")

```

\newpage
# Baseline characteristics

```{r, echo=FALSE, message=FALSE, warning=FALSE}
df$Age[4] <- NA
tbl1_func(df,c("Age"),c("Gender","Nationality","School","Parental status"),"group")

```

\newpage
# Feasibility outcomes

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 3, fig.width = 7, fig.align = "center"}

f1 <- feasibility_outcome(sum(df$`Completion of follow-up`), n, "A) Completion of follow-up", 0.68)
f2 <- feasibility_outcome(n, screened, "B) Eligible participants who consent to inclusion and randomisation", 0.29)
f3 <- feasibility_outcome(sum(df$Compliance, na.rm=T), n/2, "C) Compliance", 0.45)

grid.arrange(f1$fig,f2$fig,f3$fig,ncol=1)

ft <- data.frame(rbind(
   c(f1$name,f1$perc_requirement,f1$perc_mean,f1$perc_lcl,f1$perc_ucl),
   c(f2$name,f2$perc_requirement,f2$perc_mean,f2$perc_lcl,f2$perc_ucl),
   c(f3$name,f3$perc_requirement,f3$perc_mean,f3$perc_lcl,f3$perc_ucl)),check.names = F)
colnames(ft) = c("Outcome","Requirement","Fraction", "LCL", "UCL")

FitFlextableToPage(flextable(ft))

```

\newpage
# Exploratory clinical outcomes

## DSHI-Y (primary)
Data on non-suicidal self-injury (NSSI) as measured by DSHI-Y will be obtained in both groups at baseline and follow-up, and during the intervention for the interventional group. DSHI-Y reflects the number of NSSI events in the past month. The results will be presented as one sum score. 

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var <- "DSHI-Y"
tbl_cont_func(df,var)
result <- lin_reg(df,paste0(var," \\("))

fig_lin_assumptions(result, name=var)

fig_num_cont(df, var, " ", var,"median")  + labs(tag="A")

temp <- rbind(
   c(var, result$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## Kidscreen-10 (secondary)
Data on Kidscreen-10 will be obtained in both groups at baseline and follow-up. Kidscreen-10 has 10 items which each generates a score from 1 to 5. The sum of the raw scores will be processed using the algorithm below:

* *RASCH PP* =  ( 10 = -4.327 ) / ( 11 = -3.206 ) / ( 12 = -2.675 ) / ( 13 = -2.319 ) / ( 14 = -2.049 ) / ( 15 = -1.831 ) / ( 16 = -1.645 ) / ( 17 = -1.483 ) / ( 18 = -1.339 ) / ( 19 = -1.207 ) / ( 20 = -1.085 ) / ( 21 = -0.971 ) / ( 22 = -0.863 ) / ( 23 = -0.760 ) / ( 24 = -0.660 ) / ( 25 = -0.563 ) / ( 26 = -0.468 ) / ( 27 = -0.374 ) / ( 28 = -0.281 ) / ( 29 = -0.187 ) / ( 30 = -0.093 ) / ( 31 = 0.002 ) / ( 32 = 0.100 ) / ( 33 = 0.199 ) / ( 34 = 0.302 ) / ( 35 = 0.409 ) / ( 36 = 0.520 ) / ( 37 = 0.637 ) / ( 38 = 0.760 ) / ( 39 = 0.891 ) / ( 40 = 1.031 ) / ( 41 = 1.183 ) / ( 42 = 1.348 ) / ( 43 = 1.529 ) / ( 44 = 1.732 ) / ( 45 = 1.961 ) / ( 46 = 2.226 ) / ( 47 = 2.545 ) / ( 48 = 2.951 ) / ( 49 = 3.533 ) / ( 50 = 4.703 )

*(points = sub-score)*

The results are presented using two scales:

* **General HRQoL index** = RASCH PP
* **General HRQoL index European T-values** = (((RASCH PP - 1.2078) / 1.03377) * 10 + 50)

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var_b <- "Kidscreen-10 T-values"

df[3,grepl(var_b,colnames(df))] <- NA

tbl_cont_func(df,var_b)
result_b <- lin_reg(df,paste0(var_b," \\("))

fig_lin_assumptions(result_b, name=var_b)

fig_num_cont(df, paste0(var_b," \\("), " ", var_b,"mean")

temp <- rbind(
   c(var_b, result_b$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## DASS-21 (secondary)
Data on DASS-21 will be obtained in both groups at baseline and follow-up. DASS-21 has 21 items which each generates a score from 0 to 3. The results will be presented as sum-score for the following three subscales: 

* **Depression** = I3 + I5 + I10 + I13 + I16 + I17 + I21
* **Anxiety** = I2 + I4 + I7 + I9 + I15 + I19 + I20
* **Stress** = I1 + I6 + I8 + I11 + I12 + I14 + I18

*I: Items*

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var   <- "DASS-21"
var_a <- "DASS-21 Depression"
var_b <- "DASS-21 Anxiety"
var_c <- "DASS-21 Stress"
tbl_cont_func(df,var)
result_a <- lin_reg(df,paste0(var_a," \\("))
result_b <- lin_reg(df,paste0(var_b," \\("))
result_c <- lin_reg(df,paste0(var_c," \\("))

fig_lin_assumptions(result_a, name=var_a)
fig_lin_assumptions(result_b, name=var_b)
fig_lin_assumptions(result_c, name=var_c)

fig_num_cont(df, paste0(var_a," \\("), " ", var_a,"mean")
fig_num_cont(df, paste0(var_b," \\("), " ", var_b,"mean")
fig_num_cont(df, paste0(var_c," \\("), " ", var_c,"mean")

temp <- rbind(
   c(var_a, result_a$lin_p),
   c(var_b, result_b$lin_p),
   c(var_c, result_c$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## Self-injury (secondary)
Data on 'Self-injury' wil be obtained in both groups only at follow-up. 'Self-injury' is answered as either 'yes' or 'no'.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var   <- "Self-injury"
tbl_cat_func(df,var)
result <- log_reg(df,var)

temp <- data.frame(rbind(
   c(var, "OR", result$or_table[1,]),
   c(var, "RR", result$rr_table[1,])))
colnames(temp) <- c("var"," ", "R", "lcl", "ucl", "p")
temp$R <- round(as.numeric(temp$R),digits=2)
temp$lcl <- round(as.numeric(temp$lcl),digits=2)
temp$ucl <- round(as.numeric(temp$ucl),digits=2)
temp$p <- round(as.numeric(temp$p),digits=3)


FitFlextableToPage(flextable(temp))

```

**NB:** Confidence intervals of RR are *Unconditional MLE & normal approximation (Wald) CI*, while the confidence intervals for RR will be obtained using marginal effects.

\newpage
## Sick days (secondary)
Data on 'Sick days' wil be obtained in both groups at baseline and follow-up. 'Sick days' will be presented as a ratio, where 0 refers to full student capacity.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var <- "Sick days"
tbl_cont_func(df,var)
result <- lin_reg(df,paste0(var," \\("))

fig_lin_assumptions(result, name=var)

fig_num_cont(df, var, " ", var,"median")  + labs(tag="A")

temp <- rbind(
   c(var, result$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## DERS-16 (further)
Data on DERS-16 will be obtained in both groups at baseline and follow-up, and during the intervention for the interventional group. DERS-16 has 16 items which each generates a score from 1 to 5. The results will be presented as one sum-score. The scores in this scale range from 16-80 with higher scores indicating greater emotion regulation difficulties. 

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var   <- "DERS-16"
tbl_cont_func(df,var)
result <- lin_reg(df,paste0(var," \\("))

fig_lin_assumptions(result, name=var)

fig_num_cont(df, paste0(var," \\("), " ", var,"mean")

temp <- rbind(
   c(var, result$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## BSL-supplement (further)
Data on BSL-supplement will be obtained in both groups at baseline and follow-up, and during the intervention for the interventional group. BSL-supplement has 11 items which each generates a score from 0 to 4. The results will be presented as one sum-score. 

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

var   <- "BSL-supplement"
tbl_cont_func(df,var)
result <- lin_reg(df,paste0(var," \\("))

fig_lin_assumptions(result, name=var)

fig_num_cont(df, paste0(var," \\("), " ", var,"mean")

temp <- rbind(
   c(var, result$lin_p))
colnames(temp) <- c(" ","p-value")

df_to_linreg(data.frame(temp, check.names=F))

```

\newpage
## CCNES-APP (further)
Data on CCNES-APP will be obtained from the participants in both groups only at follow-up. CCNES-APP has 9 main items with 6 sub items (a to f) for each. Each sub item generates a score from 1 to 7. The results will be presented as mean-scores for the following six subscales:  

* **Distress reaction** = ( I1a + I2d + I3f + I4d + I5a + I6b + I7f + I8a + I9d ) / 9
* **Punitive reactions** = ( I1e + I2f + I3b + I4c + I5e + I6c + I7b + I8e + I9c ) / 9
* **Expressive encouragment** = ( I1b + I2c + I3e + I4f + I5b + I6d + I7e + I8b + I9e ) / 9
* **Emotion-focused reactions** = ( I1c + I2b + I3c + I4a + I5c + I6f + I7d + I8c + I9a ) / 9
* **Problem-focused reactions** = ( I1f + I2e + I3a + I4b + I5f + I6e + I7a + I8f + I9b ) / 9
* **Minimization reactions** = ( I1d + I2a + I3d + I4e + I5d + I6a + I7c + I8d + I9f ) / 9

*I: Items*

### Results

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

tbl_cont_func(df,"CCNES-APP")
result_di <- MWU_test(df,"CCNES-APP Distress reaction")
result_pu <- MWU_test(df,"CCNES-APP Punitive reactions")
result_ex <- MWU_test(df,"CCNES-APP Expressive encouragment")
result_em <- MWU_test(df,"CCNES-APP Emotion-focused reactions")
result_pr <- MWU_test(df,"CCNES-APP Problem-focused reactions")
result_mi <- MWU_test(df,"CCNES-APP Minimization reactions")

temp <- rbind(
   c("Distress reaction", result_di$est_ci, result_di$p),
   c("Punitive reactions", result_pu$est_ci, result_pu$p),
   c("Expressive encouragment", result_ex$est_ci, result_ex$p),
   c("Emotion-focused reactions", result_em$est_ci, result_em$p),
   c("Problem-focused reactions", result_pr$est_ci, result_pr$p),
   c("Minimization reactions", result_mi$est_ci, result_mi$p))
colnames(temp) <- c(" ","Estimate (95% Confidence interval)","p-value")

df_to_mwu(data.frame(temp,check.names=F))

```

\newpage
## NEQ (further)
Data on NEQ will be obtained in both groups only at follow-up. NEQ has 20 items, with 5 sub-items The results will be presented as means and standard deviations: 

* **Frequency negative effects** = I1a + I2a + I3a + I4a + I5a + I6a + I7a + I8a + I9a + I10a + I11a + I12a + I13a + I14a + I15a + I16a + I17a + I18a + I19a + I20a *(Score from 0 to 1)*

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 2, fig.width = 7, fig.align = "center"}

tbl_cont_func(df,"NEQ")
var_1 <- "NEQ Freq. negative effects  "

result_1 <- MWU_test(df,var_1)

temp <- data.frame(rbind(
   c(var_1, result_1$est_ci, result_1$p)), check.names = F)
colnames(temp) <- c(" ","Estimate (95% Confidence interval)","p-value")

df_to_mwu(data.frame(temp,check.names=F))
```